---
title: "Enumerate-like functionality"
author: "Nassim Haddad"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Enumerate}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

When using loop-like constructs, either via a regular `for` loop, or with `lapply`, you normally have to choose between iterating over the object itself or over its index.  
The idea of what follows is to offer you the possibility to have both at once.

## Option 1: use `enumerate()`

`enumerate()` enriches the object of the for-loop with the iteration number, which can then be accessed via `i_()`. Here is an example:

```{r}
random_numbers <- rnorm(3)
print(random_numbers)
```

```{r}
library(ETLtools)
for (x in enumerate(random_numbers)){
  print(list(iteration = i_(x), value = x))
}
```

## Option 2: use `enumapply()`

A more "R-ish" way of looping is via the apply-family. To match this style you can use `enumapply()`. The index will be passed to the function as a second argument.

```{r}
enumapply(rnorm(3), function(x, i)list(iteration = i,value = x))
```
